---
title: "Density"
author: "jafshin"
date: "15/06/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Packages
library(rdist)
library(dplyr)
library(ggplot2)
library(readr)

source("./functions/initation_functions.R")
source("./functions/land_updating.R")
source("./functions/visualisation.R")
source("./functions/make_pixels_df.R")
source("./functions/distribute_population.R")
```

## Experiment 2: Finding the density

The aim of this experiment is to find at what density there will be enough 20 min coverage given fix number of destinations. 

Steps:

 - Total population is given
 - Calculating the number of destinations based on the total population
 - Distributing the individuals
 - Finding the best locations

```{r Control Variables}



pphh <- 2.6
pop <- 30000
mutation_p <- 0.20
total_iters <- 500

share_land_for_dest <- 0.25
share_land_for_resid <- 0.7
pxl_d <- 0.2
nbhd_d <- 1.6

catchment_treshold <- 0.8

dph <- 15




```

```{r Reading inputs}

destinations <- read_csv("../inputs/destinations_v3.csv", col_names = T)

```

### How many of each destination is needed?
```{r}

destinations <- destinations %>% 
  mutate(num_net = ceiling(pop/capacity)) %>% 
  mutate(num_adj = ceiling((pop*coverage)/capacity))

destinations %>% summarise(sum_net = sum(num_net),
                           sum_adj = sum(num_adj))
glimpse(destinations)

```

## Building the neighbourhoods


TODO:
 1. Adding those incorporating within the others
 2. Adding those should be adjacent
 3. Adding those should be at the town centre or futher away
 4. Apply density to net dev area and not to the total

```{r nbhds building}

print(paste("******************* DWELLING DENSITY:", dph, sep = " "))
  
  init_nbhd <- read.csv("../inputs/neighbourhoods.csv")
  init_loc <- read.csv("../inputs/locations.csv")
  init_dest <- read.csv("../inputs/destinations_v3.csv")
  
  output_sub_dir <-  paste(output_dir, "Density_", dph, "/", sep = "")
  ifelse(!dir.exists(output_sub_dir), dir.create(output_sub_dir), FALSE)
  log_file <- paste(output_sub_dir, "output_log_D", dph, ".txt", sep = "") 
  output_file <- paste(output_sub_dir, "output_decision_D", dph, ".csv", sep = "")
  cat("", file = log_file, append = FALSE)
  
  
  cat(paste("Total Population", pop, sep = ","),  file = log_file, append = , sep="\n")
  cat(paste("Dweling Density", dph, sep = ","),  file = log_file, append = TRUE, sep="\n")
  cat(paste("***********", "***********", sep = ","),  file = log_file, append = TRUE, sep="\n")
  
  # CALCUALTING NUMBER OF NEIGHBOURHOODS
  
  pxl_a <- 0.2*0.2
  pxl_dev_a <- pxl_a * share_land_for_resid
  pxl_n <- ceiling(pop * 0.01 / (dph * pphh * pxl_dev_a))

  # How many pixels?
  nbhd_a <- nbhd_d * nbhd_d # As squares (sq.km)
  nbhd_dev_a <- nbhd_a * share_land_for_resid # As squares (sq.km)

  #nbhd_a <- 0.4*0.4*pi # As circles (sq.km)
  nbhd_n <- ceiling(pop * 0.01 / (dph * pphh * nbhd_dev_a))
  nbhd_p <- round(pop / nbhd_n)
  
  # Creating the neighbourhoods ---------------------------------------------
  init_pixls <- make_pixels_df(pxl_d, nbhd_n, share_land_for_dest, pop, dph, person_per_hh, init_dest)

  avg_px_pop <- ceiling (pop / pxl_n)

  init_pixls <- distribute_population(avg_px_pop, init_nbhd, init_pixls, pop, init_dest)
  # Selecting only occupied pixels
  init_pixls <- init_pixls %>% filter(pop > 0)
  # Adding Land
  for (i in 1:nbhd_n){
    init_nbhd$remaining_land_for_dest[i] <- init_nbhd$land_for_dest[i] <- nbhd_a * share_land_for_dest
  }
  
  for (nb in init_nbhd$ID) {
    init_nbhd$pop[nb] <- init_pixls %>% 
                          filter(nbhd == nb) %>% 
                          summarise(pop = sum(pop)) %>%
                          select(pop)
  }
  
  init_nbhd$pop <- init_nbhd$pop %>% unlist()
  
  # Creating the locations ---------------------------------------------
  
  init_loc <- make_location_df_methdod_2(init_loc, init_dest, init_nbhd[which(init_nbhd$pop>0),] )
  #init_loc <- make_location_df_methdod_2(init_loc, init_dest, init_pixls[which(init_pixls$pop>0),] )
  
  # Creating the decision dataframe --------------------------
  init_deci <- make_decsion_df(init_loc,init_dest)
  
  # Calculating distances between selection points --------------------------
  init_deci <- add_distances(init_deci, init_pixls[which(init_pixls$pop>0),])
  init_deci <- add_decision_vars(init_deci, init_pixls[which(init_pixls$pop>0),])
  # Soring init dest based on pop_req*land_req_sqkm
  
  init_dest <- init_dest %>%
                mutate(pop_land_score = pop_req*land_req_sqkm) %>%
                mutate(pop_land_weigh = pop_land_score/sum(pop_land_score)) %>%
                arrange(desc(pop_land_weigh)) %>%
                select(-pop_land_score)

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
